Figures and tables for paper

### 2023-05-16 analysis/04_figs-tables.Rmd
Moved model fit to 04_figs-table

    here::here("data", "raw_data", "posterior_draws", "intercept.rds")

@@

@@

>>>>

    # here::here("data", "raw_data", "posterior_draws", "intercept.rds")
    here::here("data", "raw_data", "posterior_draws", "index_intercept.rds")

@@

# Name levels labels
# level_labels <- c(
#   str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
#   str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
#   str_c("Organizational practices: ", c("Financial transparency", "Accountability")),
#   str_c("Funding sources: ", c("Handful of wealthy private donors", "Government grants")),
#   str_c("Relationship with host government: ", c("Criticized", "Under crackdown"))
# )

# Name levels labels (index-coded)
level_labels <- c(
  str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
  str_c("Issue area: ", c("Emergency response", "Environment", "Human rights", "Refugee relief")),
  str_c("Organizational practices: ", c("Financial transparency", "Accountability")),
  str_c("Funding sources: ", c("Many small private donations", "Handful of wealthy private donors", "Government grants")),
  str_c("Relationship with host government: ", c("Friendly", "Criticized", "Under crackdown"))
)

@@

# Compute model fit

## Load model output

```{r load-data-output, warning=FALSE, message=FALSE, eval=FALSE}
# Load all model output
intercept_run <- read_rds(here::here("data", "raw_data", "model_runs", "intercept.rds"))
public_affairs_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_affairs.rds"))
political_ideology_run <- read_rds(here::here("data", "raw_data", "model_runs", "political_ideology.rds"))
social_views_run <- read_rds(here::here("data", "raw_data", "model_runs", "social_views.rds"))
charity_voluntarism_run <- read_rds(here::here("data", "raw_data", "model_runs", "charity_voluntarism.rds"))
demographics_run <- read_rds(here::here("data", "raw_data", "model_runs", "demographics.rds"))
public_political_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political.rds"))
public_political_social_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social.rds"))
public_political_social_charity_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social_charity.rds"))
public_political_social_charity_demo_run <- read_rds(here::here("data", "raw_data", "model_runs", "public_political_social_charity_demo.rds"))
```

## Compute and save model fit

```{r compute-fit, eval=FALSE}
# Compute fit using PSIS-LOO
intercept_loo <- loo(intercept_run$fit, save_psis = TRUE)
public_affairs_loo <- loo(public_affairs_run$fit, save_psis = TRUE)
political_ideology_loo <- loo(political_ideology_run$fit, save_psis = TRUE)
social_views_loo <- loo(social_views_run$fit, save_psis = TRUE)
charity_voluntarism_loo <- loo(charity_voluntarism_run$fit, save_psis = TRUE)
demographics_loo <- loo(demographics_run$fit, save_psis = TRUE)
public_political_loo <- loo(public_political_run$fit, save_psis = TRUE)
public_political_social_loo <- loo(public_political_social_run$fit, save_psis = TRUE)
public_political_social_charity_loo <- loo(public_political_social_charity_run$fit, save_psis = TRUE)
public_political_social_charity_demo_loo <- loo(public_political_social_charity_demo_run$fit, save_psis = TRUE)

# Compare model fit
loo_compare(intercept_loo, public_affairs_loo, political_ideology_loo, social_views_loo, charity_voluntarism_loo, demographics_loo, public_political_loo, public_political_social_loo, public_political_social_charity_loo, public_political_social_charity_demo_loo)
```

```{r save-fit, eval=FALSE}
# Create data frame
model_fit <- tibble(model = rep(NA, 10), elpd_loo = rep(NA, 10))

# Extract PSIS-LOO fit
model_fit$model[1] <- "intercept"; model_fit$loo[1] <- intercept_loo$elpd_loo
model_fit$model[2] <- "public_affairs"; model_fit$loo[2] <- public_affairs_loo$elpd_loo
model_fit$model[3] <- "political_ideology"; model_fit$loo[3] <- political_ideology_loo$elpd_loo
model_fit$model[4] <- "social_views"; model_fit$loo[4] <- social_views_loo$elpd_loo
model_fit$model[5] <- "charity_voluntarism"; model_fit$loo[5] <- charity_voluntarism_loo$elpd_loo
model_fit$model[6] <- "demographics"; model_fit$loo[6] <- demographics_loo$elpd_loo
model_fit$model[7] <- "public_political"; model_fit$loo[7] <- public_political_loo$elpd_loo
model_fit$model[8] <- "public_political_social"; model_fit$loo[8] <- public_political_social_loo$elpd_loo
model_fit$model[9] <- "public_political_social_charity"; model_fit$loo[9] <- public_political_social_charity_loo$elpd_loo
model_fit$model[10] <- "public_political_social_charity_demo"; model_fit$loo[10] <- public_political_social_charity_demo_loo$elpd_loo

# Save model output
write_rds(model_fit, here::here("analysis", "output", "tables", "model_fit.rds"))
```
